\sysfull

### 2017-08-06 paper/evaluation.tex

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp}, i.e. build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller, and TI's MSP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} (hardware type will be specified per experiment in Section~\ref{sec:results_evaluation}). WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet}. FET was also used as a power supply in non-intermittent power experiment. To measure energy consumption of all benchmark applications (please refer to Section~\ref{sec:results_software}) Carnegie Mellon's EDB~\cite{edb} was used. In experiments involving wireless power, WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. RFID reader is controlled by a PC running Ubuntu 10.4 executing open source Python-based \emph{sllurp} library~\cite{sllrp_github} enabling low-level RFID reader control. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance controlled experiments, WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code completion measurements have been performed using Salea~\cite{saleae} digital logic analyzer.

@@

Expected results:
\begin{itemize}
	\item Sensitivity plot---normalized page swapping cost ("bathtub" curve) in terms of execution time: compare against Chain and full double buffering approach; show number of page swaps---do the experiment for all applications
\end{itemize}

\todo{Provide argument for page swapping using hardware support}{Brandon}

>>>>

In all experiments we used the following computing hardware: WISP\,5.1~\cite{wisp5,wisp}, i.e. build around MSP430FR5969~\cite{wolverine} 64\,kB FRAM microcontroller, and TI's MSP430FR5969 launchpad~\cite{MSP-EXP430FR5969_launchpad} (hardware type will be specified per experiment in Section~\ref{sec:results_evaluation}). WISP\,5.1 has been re-programmed during experiments using TI's Flash Emulation Tool (FET)~\cite{fet} with TI Code Composer Studio version X~\cite{}\todo{Report on CCS version; CMUs environment}{Kiwan/Amjad}. FET was also used as a power supply in non-intermittent power experiment. To measure energy consumption of all benchmark applications (please refer to Section~\ref{sec:results_software}) Carnegie Mellon's EDB~\cite{edb} was used. In experiments involving wireless power, WISP was powered through an RFID reader (Impinj R1000 with firmware version 3.2.4.240~\cite{r1000_data_sheet}) connected to Liard RFMAX S9028PCRJ 8\,dBic~\cite{atlas2015}. RFID reader is controlled by a PC running Ubuntu 10.4 executing open source Python-based \emph{sllurp} library~\cite{sllrp_github} enabling low-level RFID reader control. Transmitted power of the RFID reader was 30\,dBm at 915\,MHz center frequency. For distance controlled experiments, WISP was positioned at varying length hollow paper tubes placed directly on a flat lying antenna. Code completion measurements have been performed using Salea~\cite{saleae} digital logic analyzer.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/pagSizeOverhead}
	\caption{Normalized page size overhead and page faults per benchmark.\todo{Figure placeholder---will be replaced with final one}{Amjad}}
	\label{fig:IPOSPerformance}
	\label{fig:page_size}
\end{figure}

Figure~\ref{fig:page_size} presents the result on the effect of page swap size on the execution time of the programs executed by \sys. Overhead has been measured in the MCU clock cycles with values provided by TI CCS. Result has been normalized per benchmark: for the overhead results---to the minimum obtained value and for page faults---to the third measured maximum value\todo{Check again}{Amjad}. A subset of applications has been selected for evaluation. Additionally, page faults have been measured. The result show clearly a bathtub-shape bar plot for each application, demonstrating that for each application there is always a page size that minimizes \emph{both} execution time and page swaps. For all applications (except for Sort) this value equals roughly to 64 bytes. The shape of each figure can be explained as follows. For small page sizes (<64) the execution time is dominated by the \emph{frequency} of page swaps (each swap takes non-zero time, as shown in Figure~\ref{fig:dmaTimeEnergy}). On the other hand, in the opposite case the execution time is dominated by the time of swapping of one large page from SRAM to FRAM. Another interesting observation is the non-symmetric shape of each bar plot. This is due the size of data manipulated by the program: minimum point of overhead equals roughly to the size of the variables manipulated by each benchmark. Worth noting is also large discrepancy between minimum and maximum overhead for each benchmark (e.g. for Cuckoo 8 (at 16 bytes) to 1 (at 64 bytes), BC: 1 (at 16 bytes) to $\approx$2 (at 1024 bytes)). \todo{Explain this phenomenon}{Amjad}
